\documentclass[10.99pt]{article}
\usepackage[margin=0.65in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{fontawesome}
\usepackage{hyperref}
\pagenumbering{gobble}

\DeclareTextCommandDefault{\nobreakspace}{\leavevmode\nobreak\ }
% \hypersetup{colorlinks = true, urlcolor = blue}

\titlespacing*{\section}{0pt}{12pt plus 4pt minus 2pt}{-9pt}
\setlist[itemize]{topsep=4pt,after=\newline}

\title{\vspace{-3.5em}\textbf{Giovanni Valencia}\vspace{-0.5em}}
\author{Chicago, IL $\mid$ 708-955-9737 $\mid$ \href{mailto:giovannivalencia1694@gmail.com}{giovannivalencia1694@gmail.com}}
\date{\vspace{-2em}}

\begin{document}
\maketitle

%%%%%%%%%%%%%%
% EDUCATION %
%%%%%%%%%%%%%%
\vspace{-0.5em}
\section*{\textbf{EDUCATION}}
\noindent\makebox[\linewidth]{\rule{7.2in}{0.4pt}}
\textbf{University of Illinois at Chicago (UIC)} \hfill Chicago, IL
\\\textit{Bachelor of Science in Computer Science} \hfill Graduated May 2018

%%%%%%%%%%%%
% PROJECTS %
%%%%%%%%%%%%
\vspace{-0.5em}
\section*{PROJECTS}
\noindent\makebox[\linewidth]{\rule{7.2in}{0.4pt}} 
\vspace{-2.25em}
% COL 1
\begin{minipage}[t]{0.5\textwidth}
\raggedright
% \vspace{0.5em}
\textbf{Silent Assassin}: Java, Kotlin, XML on Android Studio using Google Maps API
\\Geolocation-based mobile game, "assassin" players attempt to capture others and engage in small battle sub-games.
\vspace{1em}
\end{minipage}
\hspace{1em}
% COL 2 (don't put a line break here)
\begin{minipage}[t]{0.5\textwidth}
\raggedright
% \vspace{0.5em}
\textbf{Dark Echo 2}: C\#, Unity engine
\\Video game based on usage of sounds waves to analyze environment and traverse game levels. Includes sound functionality, AI development, and physics. Built for 
\\HTC Vive, VR-compatible.
\vspace{1em}
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
\vspace{2.0em}
\raggedright
\textbf{Card Database}: Azure, SQL, C\# using Visual Studios
\\Robust database system for Magic: the Gathering cards, with insert and search functionalities on all card attributes, including queried price history. Multi-user capabilities with Transactional and privilege-control mechanisms.
\end{minipage}
\hspace{1em}
\begin{minipage}[t]{0.5\textwidth}
\vspace{2.0em}
\raggedright
\textbf{Text to XML Converter}: C\#, XML
\\Program made for internal usage at Logistyx. The 
\\program takes the txt file, parses it, then converts it to 
\\a specific XML format so it can be read by the 
\\proprietary software. Made specifically for International Rates to prevent time loss from creating the XML manually. Designed in a way to allow easy changes once 
\\a standard is finalized.
\end{minipage}

%%%%%%%%%%%%%%
% EXPERIENCE %
%%%%%%%%%%%%%%
\vspace{-0.5em}
\section*{\textbf{EXPERIENCE}}
\noindent\makebox[\linewidth]{\rule{7.2in}{0.4pt}}
%%%%%%%%%%%%
% Logistyx Technologies
%%%%%%%%%%%%

\noindent\textbf{Logistyx Technologies} \hfill Rolling Meadows, IL
\\\textit{Support Engineer} \hfill January 2019 - Present
\begin{itemize}
\itemsep0em
\item Directly assisted clients with issues, concerns, and change requests concerning proprietary software.
\item Developed and maintained large array of internal tools and scripts in \textless languages/frameworks\textgreater.
\item Collaborated with support team to tackle production issues, and developed processes to ensure future security.
\end{itemize}

%%%%%%%%%%%%
% UIC ACCC
%%%%%%%%%%%%
\vspace{0.5em}
\noindent\textbf{UIC ACCC - OnSite Support} \hfill Chicago, IL
\\\textit{Computer Technician/Consultant} \hfill August 2016 - December 2018
\begin{itemize}
\itemsep0em
\item Solve faculty technical issues using a ticket-based management system.
\item Manage user access, permissions, and email systems on Microsoft Active Directory.
\item Assist co-workers in diverse range of projects, including web form design, systems migrations, and physical infrastructure.
\end{itemize}

%%%%%%%%%%%%
% optum
%%%%%%%%%%%%
\vspace{0.5em}
\noindent\textbf{United Health Group - Optum Technology} \hfill Schaumburg, IL
\\\textit{Technology Development Intern} \hfill June 2017 - August 2017
\begin{itemize}
\itemsep0em
\item Collaborate with Business Analysis and Software Engineering teams to plan product development.
\item Meet with clients remotely to gather requirements and communicate product roadmaps.
\item Assist Development team with critical bug fixes in production software, involving HTML and Javascript.
\end{itemize}

%%%%%%%%%%
% SKILLS %
%%%%%%%%%%
\vspace{-2em}
\section*{SKILLS}
\noindent\makebox[\linewidth]{\rule{7.2in}{0.4pt}} 
\vspace{-2.5em}
\begin{multicols}{2}
% COL 1
\noindent\textbf{PROGRAMMING LANGUAGES}
\\Java, C/C++/C++11/C\#, SQL, XML
\\HTML, PHP, Javascript Kotlin
\\Android Studio, UNITY
\\
\begin{minipage}[t]{0.5\textwidth}
\raggedright\textbf{OTHER SKILLS}
\\Proficient in English and Spanish
\\Advanced computer repair/troubleshooting
\end{minipage}
\columnbreak
\end{multicols}

\end{document}

